\section{Turbulence Onset as a Regime I \texorpdfstring{$\to$}{to} II Transition}
\label{sec:turbulence_onset}

\begin{objectivebox}
\begin{itemize}
    \item Model turbulence onset as a Regime~I $\to$ II transition where the critical Reynolds number maps to the saturation threshold.
\end{itemize}
\end{objectivebox}

\textit{Note: This section covers the Regime I $\to$ II transition (onset). For the Regime III boundary and the resolution of the Kolmogorov cascade singularity, see Volume 3, Chapter Volume 3, Chapter 16.}

\subsection{Hypothesis}

The laminar-to-turbulent transition in fluid flow occurs at a
critical Reynolds number $\mathrm{Re}_c$ that depends on geometry.
The AVE framework identifies this transition as the Regime~I $\to$
Regime~II boundary crossing, where the driving parameter (flow
velocity, or equivalently the viscous stress) exceeds the first
universal regime boundary $r_1 = \sqrt{2\alpha}$.

The Reynolds number maps to a normalised drive parameter:
\begin{equation}
  r = \frac{\mathrm{Re}}{\mathrm{Re}_{\max}},
\end{equation}
where $\mathrm{Re}_{\max}$ is the geometry-dependent maximum
stable Reynolds number.  The universal prediction is that the
onset of turbulence (first appearance of self-sustaining vortical
structures) occurs at $r = r_1 = \sqrt{2\alpha} \approx 0.1208$.

\subsection{Mapping to Fluid Variables}

The regime boundary $r_1$ sets the ratio of inertial driving to
viscous dissipation at which the laminar standing wave (Poiseuille
flow) first saturates and begins to shed energy into higher modes
(turbulent eddies).  The saturation operator governs the
transition:
\begin{equation}
  S(\mathrm{Re}, \mathrm{Re}_c)
  = \sqrt{1 - \left(\frac{\mathrm{Re}}{\mathrm{Re}_c}\right)^2}.
\end{equation}
For $\mathrm{Re} < \mathrm{Re}_c$, $S > 0$ and the flow remains
laminar.  At $\mathrm{Re} = \mathrm{Re}_c$, $S = 0$ and the
laminar mode is fully saturated.

\subsection{Testable Prediction}

The intermittency fraction (fraction of time the flow exhibits
turbulent bursts) near the critical Reynolds number should follow
$1 - S(\mathrm{Re}, \mathrm{Re}_c)$, measurable via hot-wire
anemometry in pipe flow at controlled Reynolds numbers.

\begin{summarybox}
\begin{itemize}
    \item Turbulence onset is modelled as a Regime~I $\to$ II transition: the critical Reynolds number $\mathrm{Re}_c$ maps to the saturation threshold $S(\mathrm{Re}, \mathrm{Re}_c)$, predicting intermittent turbulent bursts near the transition boundary.
\end{itemize}
\end{summarybox}

\begin{exercisebox}
\begin{enumerate}
    \item Design a hot-wire anemometry experiment to verify that turbulent burst statistics near $\mathrm{Re}_c$ follow the saturation function $1 - S(\mathrm{Re}, \mathrm{Re}_c)$.
\end{enumerate}
\end{exercisebox}

