\chapter{Universal Saturation-Kernel Catalog --- Axiom 4 at All Scales}
\label{app:universal_saturation_kernel}

\textit{One kernel governs every topological-reorganization event in the universe.}

\vspace{1em}

Per the A-034 canonical synthesis (2026-05-15 evening),
Axiom~4's saturation kernel
\begin{equation}
S(A) = \sqrt{1 - A^2}
\label{eq:universal_kernel}
\end{equation}
governs the substrate's nonlinear response to local strain $A$ normalized
to its saturation limit. Per Axiom~2 (TKI scale invariance), the kernel
applies at every scale of physical phenomenon --- $A$ is the same
dimensionless quantity (substrate strain / local saturation) regardless
of whether the physical observable manifests as voltage, magnetic field,
frame-dragging strain, or something else. When $S(A) = 0$ locally, the
substrate cannot continue linear response and \emph{must reorganize
topologically} to a new configuration with $A < 1$. The kernel's
\emph{vertical tangent at $A = 1$} is what makes every reorganization
event sharp and impulsive across all scales.

This appendix catalogs the kernel's six known canonical manifestations.
Each row is a CANONICAL framework result with its primary corpus
citation; the unification across rows is A-034's contribution.

\section{Catalog: 17 canonical instances, one kernel}
\label{sec:saturation_kernel_catalog}

\textbf{Framework principle (Grant 2026-05-15 late evening):} \emph{``the
bulk response of the lattice to strain is universal.''} Per Axiom~2 (TKI
scale invariance), the substrate's bulk strain response is set by the
same kernel $\sqrt{1-A^2}$ at every scale and in every domain. Expanded
post-2026-05-15-evening cross-repo audit + Grant promotion direction
(consolidating AVE-Bench-VacuumMirror Ch~2's independently-built
catalog + 9 additional instances from sister-repo audit).

\textbf{3-way symmetry classification} per asymmetric-saturation
exploration:
\begin{itemize}
    \item \textbf{SYM} = Symmetric (vacuum $K = 2G$; $\varepsilon$, $\mu$ saturate together)
    \item \textbf{ASYM-N} = Asymmetric natural (single-sector: only $\varepsilon$ or only $\mu$)
    \item \textbf{ASYM-E} = Asymmetric engineered decoupled ($K/G \neq 2$ by design)
\end{itemize}

\subsection{Physical-substrate scales (12 rows)}

\begin{center}
\renewcommand{\arraystretch}{1.4}
\scriptsize
\begin{tabular}{|p{1.5cm}|p{0.9cm}|p{2.2cm}|p{2.5cm}|p{2.6cm}|p{2.0cm}|}
\hline
\textbf{Scale} & \textbf{Sym} & \textbf{``$A$''} & \textbf{Saturation event} & \textbf{Corpus} & \textbf{Empirical} \\
\hline
Atomic / EM & SYM & $V / V_{\text{snap}}$ & Dielectric breakdown $\to$ pair creation & Ax~4 + Vol~4 Ch~1 & Schwinger limit \\
\hline
Substrate (K4) & SYM & bond-bow / saturation & K4 lattice + soliton formation & Vol 1 Ch~\ref{ch:macroscopic_moduli} & substrate instance \\
\hline
Nuclear (DT fusion) & SYM & nodal strain / $V_{\text{yield}}$ & Topology snap; 14.1 MeV n + $^4$He $\alpha$ & AVE-Fusion Ch~1:20 & DT fusion canonical \\
\hline
Condensed matter (BCS) & \textbf{ASYM-N} ($\mu$) & $T/T_c$ & Cooper-pair form; $B_c(T) = B_{c0}\sqrt{1-(T/T_c)^2}$ & KB \texttt{ch09} leaf & \textbf{0.00\% error} \\
\hline
Plasma ($\varepsilon$-sector) & \textbf{ASYM-N} ($\varepsilon$) & $V_{\text{local}}/V_{\text{snap}}$ & Plasma cutoff ($\varepsilon_{\text{eff}} \to 0$) & $\varepsilon$-$\mu$ duality leaf & plasma canonical \\
\hline
Kolmogorov turbulence & SYM & $k/k_{\text{node}}$ & Spectral cutoff at dissipation & Bench Ch~2:159 & Kolmogorov empirical \\
\hline
Planetary (geomagnetic) & SYM & dynamo / threshold & Pole flip & Vol~3 Ch~13:131 & geology + Venus null \\
\hline
Stellar (solar flare) & SYM & twisted-flux / shear & CME / macro Zener avalanche & Vol~3 Ch~14 & \textbf{NOAA GOES 40-yr} \\
\hline
Galactic (MOND) & SYM & $g_N/a_0$ & Newtonian $\to$ deep-MOND transition & \texttt{mond.md} leaf & deep-MOND derived \\
\hline
BH event horizon & SYM & $2GM/(c^2 r)$ / 1 & $R_S$ formation: $\Gamma=-1$ & KB \texttt{ch03} leaf & \textbf{Schwarzschild exact} \\
\hline
BH merger (ring-down) & SYM & strain / $r_{\text{sat}}=7M_g$ & QNM $\omega_R M_g = 18/49$ & Vol~3 Ch~15 & \textbf{1.7\% GR; 10-18\% LIGO} \\
\hline
Cosmic (Big Bang) & SYM* & parent-BH strain / 1 & K4 crystallization seed event & A-034 NEW & CMB axis pre-reg \\
\hline
\end{tabular}
\end{center}
\textsuperscript{*}Cosmic symmetry testable via CMB E/B polarization signature.

\subsection{Biological-substrate scales (2 rows)}

\begin{center}
\renewcommand{\arraystretch}{1.4}
\scriptsize
\begin{tabular}{|p{2.4cm}|p{0.8cm}|p{2.8cm}|p{4.0cm}|p{3.2cm}|}
\hline
\textbf{Scale} & \textbf{Sym} & \textbf{``$A$''} & \textbf{Saturation event} & \textbf{Corpus} \\
\hline
Lipid bilayer membrane & SYM & strain / yield & Phase transition; cholesterol = engineered phase-buffer & AVE-Protein engine \\
\hline
Protein folding & SYM & $d_0 / d$ atomic separation & Folding snap: $C_{\text{eff}} = C_0/\sqrt{1-(d_0/d)^2}$ & AVE-Protein Vol~3 Ch~3:509 \\
\hline
\end{tabular}
\end{center}

\subsection{Engineered-substrate scales (5 rows)}

\begin{center}
\renewcommand{\arraystretch}{1.4}
\scriptsize
\begin{tabular}{|p{2.4cm}|p{0.8cm}|p{2.7cm}|p{4.2cm}|p{3.0cm}|}
\hline
\textbf{Scale} & \textbf{Sym} & \textbf{``$A$''} & \textbf{Saturation event} & \textbf{Corpus} \\
\hline
PONDER-05 quartz & SYM & $V_{\text{DC}}/V_{\text{yield}} = 0.687$ & $\varepsilon_{\text{eff}}$ collapse 27.4\%, $C_{\text{eff}}$ rise 37.7\% at 30 kV bias & AVE-PONDER Vol~4 Ch~4:17 \\
\hline
AVE-Bench-VacuumMirror & SYM & $A_{\text{DC}}(\mathbf{r})$ field profile & $\Gamma_{\text{bench}}$ from $\int \nabla S_{\text{eff}}$ along photon path & Bench Ch~2 (proposed) \\
\hline
Active topological metamaterials & \textbf{ASYM-E} & $\phi / \phi_{\text{crit}}$ & Phase crystallization V$_I$; \textbf{asymmetric saturation variant} $K/G \neq 2$ --- designer-controllable decoupled $\varepsilon/\mu$ & AVE-Metamaterials Vol~1 Ch~2:71 + Ch~4 \\
\hline
Sine-Gordon kink memory (APU) & SYM & metric displacement / yield & $2\pi$ phase kink; integer topological charge & AVE-APU Vol~1 Ch~8:14 \\
\hline
Autoresonant rupture (propulsion) & SYM & laser field / $V_{\text{snap}}$ & PLL ring-up to Schwinger-fraction rupture & AVE-Propulsion Vol~5 Ch~5:13 \\
\hline
\end{tabular}
\end{center}

\textbf{Total: 19 canonical instances of the universal kernel} (12 physical
+ 2 biological + 5 engineered). \textbf{Symmetry breakdown:} 16 SYM, 2
ASYM-N (natural single-sector --- BCS $\mu$-only and plasma
$\varepsilon$-only), 1 ASYM-E (engineered decoupled --- active topological
metamaterials).
21 orders of magnitude span with multiple validated scales. BCS
$B_c(T) = B_{c0}\sqrt{1-(T/T_c)^2}$ at 0.00\% error is the tightest
single-instance validation; BH merger ring-down at 1.7\% from GR exact
is the most direct cross-scale experimental validation.

\textbf{Explicitly kept separate (per Grant 2026-05-15 evening direction):}
LLM SiLU activation saturation (\texttt{ave-kb/...vol\_virtual\_media/ch12-sigmoid-saturation.tex}).
Same kernel form ($\sigma(x)^2 + r^2 = 1$ unit-circle derivation) but applied
in activation space during neural-net training, not as the same physical
strain-snap event. Tracked as a parallel thread.

\textbf{Explicitly flagged for follow-up:} the asymmetric saturation
variant ($K_{\text{wedge}}/G_{\text{wedge}} \neq 2$) from active topological
metamaterials --- a novel kernel topology requiring separate framework
exploration (deferred).

\section{Notes on each row}

\subsection{Atomic / EM scale: Axiom 4 in its canonical form}

The kernel's original formulation. $V$ is the local electric potential
relative to the substrate; $V_{\text{snap}}$ is the saturation voltage
(canonical $\approx 43.65$~kV per Vol~4 Ch~1, INVARIANT-C1).
At $V = V_{\text{snap}}$, $S(A) = 0$: the substrate cannot sustain
further potential without dielectric breakdown, triggering pair
creation as the topological reorganization. The Born--Infeld $n=2$
saturation form is what distinguishes the AVE substrate from
Maxwell-linear models.

\subsection{Substrate (K4) scale: substrate-scale instance of A-034}

The substrate-scale K4 micromechanics is developed in detail in
Vol 1 Ch~\ref{ch:macroscopic_moduli} (Macroscopic Moduli) as the
substrate-scale instance of A-034. The magic-angle equation
$K(u_0^*) = 2 G(u_0^*)$ IS the substrate-scale expression of
$S(A^*) = 0$. The K4 lattice + bound-state solitons ARE the
substrate's self-consistent configuration at the saturation
boundary. $\chi_K = 12$ (canonical multiplicity from
$|T| = 12$ K4 symmetry) is the substrate-scale QNM
$\ell$-mode multiplicity.

\subsection{Planetary scale: geomagnetic reversal}

Earth's spin imparts strain on the lattice via the geodynamo (Vol~3
Ch~13). The strain accumulates against a ``Baryonic phase density
threshold'' (Vol~3 Ch~13:131); when the threshold is crossed, the
field topology reorganizes via pole reversal. Average reversal
interval $\sim 200{,}000$--$300{,}000$ years (irregular, geological
record). Venus's slower spin keeps it below threshold, producing
essentially zero magnetic field --- a canonical AVE prediction.

\subsection{Stellar scale: solar flares and CME}

Differential rotation winds the $1/d$ topological displacement lattice
(``Parker Spiral'' in standard astrophysics). Strain accumulates as
the twisted flux lines store mechanical potential energy. When the
critical shear-stress threshold is crossed, the wound lattice
snaps to a lower-energy configuration: magnetic reconnection
releases the stored energy as a directional kinetic pressure wave
(CME / solar flare). Power-law size distribution follows
semiconductor avalanche-breakdown statistics (Vol~3 Ch~14 ---
``the Sun as a macroscopic LED'').

\subsection{BH merger scale: ring-down QNM}

Newly-formed BH at $r_{\text{sat}} = 7 M_g$ (Axiom 4 saturation
boundary applied to BH). The ring-down is the saturation cavity's
fundamental resonance mode. AVE prediction
$\omega_R M_g = 18/49 = 0.3673$ (1.7\% from GR exact 0.3737); 10--18\%
agreement with three LIGO events (GW150914, GW170104, GW151226).
This is the framework's most direct experimental validation of the
kernel at non-atomic scale.

\subsection{Cosmic scale: K4 crystallization seed event}

\textbf{The newest entry (Grant synthesis 2026-05-15 evening per A-034).}
A spinning parent BH in its embedding parent lattice imparts bulk
strain via frame-dragging (Vol~3 Ch~2 \S138 + Vol~3 Ch~3 \S178). The
strain extends inside the parent BH's event horizon (Kerr interior
frame-dragging continues), which IS our universe's pre-crystallization
phase per Vol~3 Ch~21. The strain pushes local $A$ toward 1 at the
point of maximum concentration (probably along the parent BH's spin
axis); at $A = 1$, $S(A) = 0$ and the substrate phase-transitions to
K4 lattice. The crystallization front propagates outward at lattice
wave speed $c$, sweeping the inherited volume which becomes our
observable universe.

This is the framework's mechanism for the Big Bang itself --- not a
separate cosmological law, but Axiom~4 applied at cosmic scale via
the universal kernel.

\section{Cross-scale validation paths}

The catalog enables testable cross-scale predictions per A-034 \S A-034.5:

\begin{itemize}
    \item CMB axis-of-evil (Planck data, $\approx (l=174^\circ, b=-5^\circ)$)
    should align with: Hubble flow anisotropy (Pantheon+); large-scale-
    structure galaxy rotation (SDSS); matter-asymmetry direction.
    Standard cosmology has no reason for these axes to align;
    A-034 predicts they MUST share the parent BH's spin axis.

    \item Universe age $R_H / c \approx 14.5$~Gyr (predicted from
    crystallization-front-at-$c$) matches observed $\sim 13.8$~Gyr
    within $\sim 5\%$.

    \item Power-law avalanche statistics at solar flare scale (Vol~3
    Ch~14 canonical) should be related to ring-down QNM frequency
    distribution and geomagnetic reversal interval distribution
    cross-scale via the kernel's universal threshold-snap behavior.

    \item CMB power-spectrum peaks should match the parent BH's QNM
    $\ell$-spectrum (Vol~3 Ch~15 scaled to cosmic scale), testable
    against Planck data.
\end{itemize}

A formal pre-registration of the multi-observable axis-alignment test
exists in the L3 electron-soliton research directory, dated 2026-05-15,
titled ``A-034 CMB Axis Alignment Empirical Prereg''.

\section{Why this matters}

Pre-A-034: each row of the catalog was treated as a separate framework
result --- Vol~3 Ch~13 had geomagnetic reversal; Vol~3 Ch~14 had solar
flares; Vol~3 Ch~15 had BH ring-down; the substrate-scale magic-angle
analysis was a separate Cosserat-moduli result; the cosmic initial
condition was framed as ``God's Hand'' inaccessible.

Post-A-034: \emph{all six rows are the same physics}, with the kernel
inherited from Axiom~4 + Axiom~2 (scale invariance) and the
phenomenology determined by the local saturation-boundary geometry.

This is the framework's largest unification to date: \emph{one kernel,
six scales, every topological reorganization event in the universe.}
The framework simplifies rather than complicates as evidence
accumulates --- the kernel doesn't change, only the lattice scale
changes.

\section{Cross-references}

Path prefix \texttt{AVE-Core/} is implicit throughout.

\begin{itemize}
    \item \textbf{Manuscript canonical:} this chapter is the catalog of
    record for the A-034 Universal Saturation-Kernel Strain-Snap
    Mechanism. Vol~3 Ch~4 \S\ref{sec:tki_strain_snap} (TKI Strain-Snap
    section) is the manuscript cosmology counterpart; Vol~3 Ch~21
    (BH interior) carries the same epistemic-horizon framing.
    \item \textbf{Substrate-scale instance:} Vol~1 Ch~\ref{ch:macroscopic_moduli}
    (Macroscopic Moduli) develops the substrate-scale K4 magic-angle
    expression of the universal kernel.
    \item \textbf{Empirical prereg} (cosmic-scale test, extended with
    E/B polarization observable): pre-registered 2026-05-15 in the
    research directory.
    \item \textbf{Asymmetric saturation variant} (3-way symmetry
    classification): same date in the research directory.
    \item \textbf{Measurement-hierarchy framing} (engineered-substrate
    rows unified): same date in the research directory. Explains why
    bench design uses many emitters (bulk-response = A-034 universal kernel
    measurement) and how single-emitter / multi-emitter / phased-array
    PLL modes connect AVE-Bench-VacuumMirror, IVIM, YBCO phased array,
    and Propulsion autoresonant rupture as the same engineered-kernel
    architecture.
\end{itemize}
