\chapter{System Verification Trace}
\label{app:verification}

The following verification log was aggregated from the AVE computational validation suite. It certifies that the fundamental limits, constants, and parameters derived in this text are calculated exclusively using exact Chiral LC continuum mechanics and rigid solid-state thermodynamic boundaries, constrained by exactly three empirical parameters.

\section*{Automated Verification Output}

\begin{verbatim}
==========================================================
AVE UNIVERSAL DIAGNOSTIC & VERIFICATION ENGINE
Dynamic Output -- Generated from src/ave/core/constants.py
==========================================================

[SECTOR 1: INITIAL HARDWARE CALIBRATION]
> Parameter 1: Lattice Pitch (l_node):  3.8616e-13 m
> Parameter 2: Dielectric Limit (alpha):    1/137.036
> Parameter 3: Macroscopic Gravity (G):  6.6743e-11 m^3/kg*s^2
> Topo-Conversion Constant (xi_topo):     4.1490e-07 C/m
> QED Geometric Packing Fraction (p_c):  0.1834
> Impedance of Free Space (Z_0):         376.73 Ohm

[SECTOR 2: BARYON SECTOR & STRONG FORCE]
> Faddeev-Skyrme Coupling (kappa_cold):  8*pi = 25.1327
> Thermal Correction (delta_th):         1/(14*pi^2) = 0.007237
> Effective Coupling (kappa_eff):        24.9508
> Dynamic I_scalar:                      1162.0 m_e
> Toroidal Halo Volume (V_halo):         2.0
> Theoretical Proton Eigenvalue:         1836.12 m_e
> Empirical CODATA Target:              1836.15268 m_e
> Deviation:                             0.0019%
> Torus Knot Ladder Spectrum:
>   (2,5)  -> 938 MeV vs Proton (938)      0.00%
>   (2,7)  -> 1261 MeV vs Delta(1232)      2.35%
>   (2,9)  -> 1582 MeV vs Delta(1600)      1.11%
>   (2,11) -> 1895 MeV vs Delta(1900)      0.27%
>   (2,13) -> 2195 MeV vs N(2190)          0.21%
>   (2,15) -> 2478 MeV vs Delta(2420)      2.40%
> Derived Confinement Force:             160,037 N (0.999 GeV/fm)
> Baseline Lattice Tension (T_EM):       0.2120 N
> Dielectric Snap Voltage (V_snap):      511.0 kV

[SECTOR 3: COSMOLOGY & DARK SECTOR]
> Asymptotic Hubble Limit (H_inf):       69.32 km/s/Mpc
> Asymptotic Hubble Time (1/H_inf):      14.105 Billion Years
> Hubble Radius (R_H):                   1.334e+26 m
> MOND Acceleration (a_0 = cH/2pi):      1.07e-10 m/s^2
> Bulk Mass Density (rho_bulk):          7.910e+06 kg/m^3

[SECTOR 4: LATTICE IMPEDANCE & MODULI]
> Poisson Ratio (nu_vac = 2/7):          0.285714
> Trace-Reversal (K = 2G):               Exact by construction
> Weak Mixing Angle (sqrt(7)/3):         0.8819

[SECTOR 5: FDTD ENGINE STATUS]
> 3D Non-Linear FDTD:                   Axiom 4 eps_eff per cell per timestep
> Linear Mode:                           Available (linear_only=True)
> Mur ABC:                               1st-Order (6 faces)
> Total Test Suite:                       62/62 PASSED

==========================================================
VERIFICATION COMPLETE: STRICT GEOMETRIC CLOSURE
168/168 framework files -- zero Standard Model parameters.
==========================================================
\end{verbatim}

\section{The Directed Acyclic Graph (DAG) Proof}
To definitively establish that the Applied Vacuum Engineering (AVE) framework possesses strict mathematical closure without phenomenological curve-fitting, the framework maps the Directed Acyclic Graph (DAG) of its derivations.

The entirety of the framework's predictive power is derived by bridging \textbf{Three Initial Hardware Parameters} with \textbf{Four Topological Axioms}.
\begin{enumerate}
    \item \textbf{Parameter 1 (The Spatial Cutoff):} The effective macroscopic spatial scale of the lattice ($\ell_{node}$). The electron mass is derived as the unknot ground-state energy: $m_e = T_{EM} \cdot \ell_{node} / c^2$.
    \item \textbf{Parameter 2 (The Dielectric Bound):} The absolute structural self-impedance of the macroscopic lattice is rigidly governed by the fine-structure constant ($\alpha$).
    \item \textbf{Parameter 3 (The Machian Boundary):} Macroscopic Gravity ($G$) acts as the structural impedance parameter defining the causal limits of the manifold.
    \item \textbf{Axiom 1 (Impedance):} The vacuum is a discrete LC resonant network with $Z_0 = \sqrt{\mu_0/\varepsilon_0}$ and lattice pitch $\ell_{node} = \hbar/(m_e c)$. Underlying mechanism: trace-free Chiral LC network supporting microrotations.
    \item \textbf{Axiom 2 (Fine Structure):} The fine-structure constant couples topology to impedance, $\alpha = e^2/(4\pi\varepsilon_0 \hbar c)$, setting the dielectric yield voltage $V_{yield} = \sqrt{\alpha}\,V_{snap}$. Underlying mechanism: topo-kinematic isomorphism $[Q] \equiv [L]$, with topological conversion constant $\xi_{topo} = e/\ell_{node}$.
    \item \textbf{Axiom 3 (Gravity):} Newton's constant emerges as the Machian boundary impedance, $G = \hbar c/(7\xi\,m_e^2)$ with $\xi \approx 8.15\times 10^{43}$ the dimensionless Machian hierarchy coupling. Underlying mechanism: minimisation of the macroscopic hardware action $S_{AVE}$ across the phase transport field $\mathbf{A}$.
    \item \textbf{Axiom 4 (Universal Saturation Kernel):} $S(A) = \sqrt{1-(A/A_{yield})^2}$ bounds all LC modes. Underlying mechanism: non-linear Born-Infeld dielectric with squared yield limit ($n=2$), aligning with the $E^4$ Euler-Heisenberg energy density and the $\chi^{(3)}$ Kerr displacement.
\end{enumerate}

From these initial geometric anchors and four structural rules, all fundamental constants dynamically emerge as the strict mechanical limits of the EFT:
\begin{itemize}
    \item \textbf{Geometry \& Symmetries (Parameters 1 \& 2):} Dividing the localized topological yield by the continuous macroscopic Schwinger yield dictates the emergence of the macroscopic fine-structure geometric constant ($1/\alpha = 8\pi/p_c$). The $\mathbb{Z}_3$ symmetry of the Borromean proton generates $SU(3)$ color symmetry, evaluating the Witten Effect to predict $\pm 1/3e$ and $\pm 2/3e$ fractional charges.
    \item \textbf{Electromagnetism (Axioms 1 \& 2):} Axiom 2's topo-kinematic mechanism yields the topological conversion constant ($\xi_{topo}$), demonstrating that magnetism is equivalent to kinematic convective vorticity ($\mathbf{H} = \mathbf{v} \times \mathbf{D}$); Axiom 1 supplies the wave dynamics propagating this charge.
    \item \textbf{The Electroweak Layer (Axioms 1 \& 2):} Axiom 1's LC network, evaluated via Effective Medium Theory (EMT) for a 3D amorphous central-force network with coordination $z_0 \approx 51.25$, shows that $K/G = 2$ at the unique operating point $p^* = 8\pi\alpha \approx 0.1834$, located $56.7\%$ above the rigidity threshold. The vacuum is a rigid solid, not a marginal glass. This trace-reversed geometric boundary forces the macroscopic vacuum Poisson's ratio to $\nu_{vac} = 2/7$, which evaluates the Weak Mixing Angle acoustic mass ratio ($m_W / m_Z = \sqrt{7}/3 \approx 0.8819$). The fine-structure value of $\alpha$ entering this constraint is fixed by Axiom 2.
    \item \textbf{Gravity and Cosmology (Axiom 3):} Projecting a 1D QED string tension into the 3D bulk metric via the trace-reversed tensor yields the $1/7$ isotropic projection factor for massive defects. Integrating the 1D causal chain across the 3D holographic solid angle, bounded by the cross-sectional porosity ($\alpha^2$) of the discrete graph, analytically binds macroscopic gravity ($G = \hbar c/(7\xi\,m_e^2)$) and the Asymptotic de Sitter Expansion Limit ($H_\infty$) into a single, unified mathematical identity.
    \item \textbf{The Dark Sector (Axiom 4):} The strict EFT hardware packing fraction ($p_c approx 0.1834$) limits excess thermal energy storage during lattice genesis, proving Dark Energy is a mathematically stable phantom energy state ($w \approx -1.0001$). The generative expansion of the lattice sets a fundamental continuous Unruh-Hawking drift. The exact topological derivation of the substrate mass density ($\rho_{bulk}$) and mutual inductance ($\nu_{vac}$) dictates a saturating Dielectric Saturation-plastic transition, mathematically recovering the exact empirical MOND acceleration boundary ($a_{genesis} = c H_\infty / 2\pi$), dynamically yielding flat galactic rotation curves without invoking non-baryonic particulate dark matter.
\end{itemize}

\subsection*{Explicit Closure DAG}

Earlier editions of this section asserted closure narratively without constructing the DAG. The acyclicity check below makes the dependency graph explicit, including back-edges that the Layer-8 closure introduces and the conditions under which it remains acyclic.

\paragraph{Layer 0 --- Inputs.}
\begin{itemize}
    \item $m_e$ (or equivalently $\ell_{node} = \hbar/(m_e c)$) --- one is the empirical input mass scale; the other is computed from it. \textbf{Status:} input scale.
    \item $\hbar, c, e, \mu_0, \varepsilon_0$ --- SI anchors (definitional under SI 2019).
    \item $T_{\text{CMB}} = 2.725\,\text{K}$ --- cosmological boundary condition.
    \item $\delta_{strain} \approx 2.225\times 10^{-6}$ --- \textbf{status: structure predicted (existence + sign of $\alpha$ thermal running below cold-lattice asymptote); magnitude at $T_{CMB}$ is one currently-fitted scalar} (back-subtracted from CODATA, pending first-principles derivation from $G_{vac}$ + equipartition). Same predicted/fitted pattern as Vol~6's $R$ per nucleus. See Ch.~\ref{ch:alpha_golden_torus} disclosure.
    \item Axioms 1--4 --- structural postulates.
\end{itemize}

\paragraph{Forward edges (conditional on Axioms 1--4).}
The forward DAG is constructed by inspection of the per-row formulas in Appendix~\ref{ch:full_derivation_chain}; representative edges:
\begin{itemize}
    \item $\ell_{node} \leftarrow \{m_e, A1\}$;\quad $\xi_{topo} = e/\ell_{node} \leftarrow \{\ell_{node}, A2\}$;\quad $T_{EM} = m_e c^2/\ell_{node}$;\quad $V_{snap} = m_e c^2/e$.
    \item $p_c = 8\pi\alpha \leftarrow \{\alpha\}$;\quad $V_{yield} = \sqrt{\alpha}\,V_{snap} \leftarrow \{\alpha, V_{snap}, A2\}$.
    \item $\nu_{vac} = 2/7 \leftarrow \{A1$ LC mechanism, $K{=}2G$ at $\alpha\}$;\quad $\sin^2\theta_W = 2/9 \leftarrow \{\nu_{vac}\}$.
    \item $M_W \leftarrow \{m_e, \alpha, p_c, \sin^2\theta_W\}$;\quad $M_Z = (3/\sqrt{7})M_W$.
    \item $G_F \leftarrow \{M_W, \sin^2\theta_W, \alpha\}$;\quad $v_{Higgs} = 1/\sqrt{\sqrt{2}\,G_F}$;\quad $m_H = v/\sqrt{N_{K4}}$.
    \item Lepton spectrum: $m_\mu \leftarrow \{m_e, \alpha, A1$ Cosserat$\}$;\quad $m_\tau \leftarrow \{m_e, \alpha, p_c\}$.
    \item $\alpha_s = \alpha^{3/7}$;\quad quark masses $\leftarrow$ functions of $\{m_e, m_\mu, m_\tau, \alpha, \alpha_s\}$.
    \item CKM $\leftarrow \{\sin^2\theta_W, \nu_{vac}\}$;\quad PMNS $\leftarrow \{\nu_{vac}, c_1, c_3\}$.
    \item $H_\infty = 28\pi m_e^3 c G/(\hbar^2 \alpha^2)$;\quad $a_0 = c H_\infty / (2\pi)$.
\end{itemize}
By inspection, the forward graph is acyclic: every derived quantity depends only on Layer-0 inputs and earlier-layer derivations.

\paragraph{Back-edges (Layer-8 closure attempts).}
The framework's ``zero free parameters'' claim requires closing the Layer-0 inputs $\{m_e, \alpha, G\}$ via back-edges:
\begin{itemize}
    \item \textbf{$\alpha$ closure (Ch.~\ref{ch:alpha_golden_torus} Golden Torus):} $\alpha^{-1}_{ideal} = 4\pi^3 + \pi^2 + \pi$ at the cold-lattice asymptote, from the trefoil's three-regime decomposition. Acyclic if the Golden Torus geometry is established independently of $\alpha$'s measured value (the three regimes are individually grounded in the chapter; this can be checked separately). The thermal running $\alpha^{-1}(T) < \alpha^{-1}_{ideal}$ at $T > 0$ is a structural prediction (sign and existence). \emph{Magnitude-derivation gap:} $\delta_{strain}$ at $T_{CMB}$ is currently back-subtracted from CODATA, definitional given the engine's \texttt{DELTA\_STRAIN = 1 - (1/ALPHA)/ALPHA\_COLD\_INV}. The cold-lattice $\alpha$ closure itself is acyclic; the magnitude of the thermal correction is fitted (one scalar) until derived from $G_{vac}$ + equipartition. Same predicted/fitted pattern as Vol~6 (predicted: structure; fitted: one scalar) --- different physics, same disclosure shape.
    \item \textbf{$m_e$ closure (Layer 8 via Nyquist):} $m_e$ becomes derivable from $\ell_{node}$ if $\ell_{node}$ is fixed by Nyquist resolution of the smallest stable soliton. Acyclic if Nyquist resolution is established independently of $m_e$ (rather than through ``the smallest soliton has rest mass $m_e$'').
    \item \textbf{$G$ closure (Layer 7 via $H_\infty$ + Axiom 3):} $G = \hbar c/(7\xi\,m_e^2)$ with $\xi = 4\pi(R_H/\ell_{node})\alpha^{-2}$. Once $\alpha$ and $m_e$ are closed and $R_H$ is set by the cosmological generation thermodynamics, $G$ follows. Acyclic conditional on the prior closures.
\end{itemize}

\paragraph{Acyclicity verdict.}
The forward DAG is acyclic. Of the three Layer-8 back-edges, the $G$ closure is acyclic conditional on the other two; the $m_e$ closure depends on whether ``smallest stable soliton'' is well-defined without circular reference to $m_e$; the $\alpha$ cold-lattice closure ($\alpha^{-1}_{ideal} = 4\pi^3+\pi^2+\pi$) is acyclic by inspection. The thermal-running magnitude $\delta_{strain}$ at $T_{CMB}$ is currently a fitted scalar (one scalar bridging cold-lattice $\alpha$ to CODATA; same predicted/fitted pattern as Vol~6's $R$ per nucleus). Deriving $\delta_{strain}$ from first principles (lattice $G_{vac}$ + equipartition) would upgrade the $\alpha$ closure from ``structure predicted, magnitude fit'' to fully zero-parameter --- that magnitude-derivation is the principal outstanding rigour gap, not a calculational error elsewhere in the chain.

Because the forward DAG is acyclic and the back-edges are individually identifiable and conditional, the AVE framework is a mathematically structured Topological Effective Field Theory whose ``zero free parameters'' claim is precisely as strong as the Layer-8 closure conditions hold. Earlier editions overclaimed this strength; the present edition documents it.

\section*{Outstanding Rigour Gaps}

The closure conditions above resolve into a small, explicit set of pending derivations. Each is documented at its inline disclosure point in the corpus and consolidated here for reference. Closing any of these strengthens the ``structurally zero-parameter'' framing toward ``absolutely zero-parameter.''

\begin{center}\small
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{p{0.18\textwidth}p{0.30\textwidth}p{0.30\textwidth}p{0.16\textwidth}}
\toprule
\textbf{Gap} & \textbf{Status} & \textbf{What closure unlocks} & \textbf{Inline disclosure} \\
\midrule
$\delta_{strain}$ magnitude at $T_{CMB}$ & One fitted scalar ($\approx 2.225 \times 10^{-6}$) currently back-subtracted from CODATA. Structure predicted (existence + sign of thermal running below the cold-lattice $\alpha$ asymptote); magnitude pending. & Upgrades the $\alpha$ closure from ``structure predicted, magnitude fit'' to absolutely zero-parameter. Requires deriving the lattice's effective thermal expansion coefficient from $G_{vac}$ + equipartition at $T_{CMB}$ and showing the predicted $\delta_{strain}$ matches the back-subtracted value. & Ch.~\ref{ch:alpha_golden_torus} status disclosure; Back-edges above. \\
$m_e$ closure via Nyquist independence & One of $\{m_e, \ell_{node}\}$ is the input scale; the other is computed via $\ell_{node} = \hbar/(m_e c)$. Layer~8 proposes Nyquist resolution of ``the smallest stable soliton'' fixes $\ell_{node}$ independently of $m_e$. & Removes the input-scale degree of freedom; both $\ell_{node}$ and $m_e$ become emergent. Requires demonstrating ``smallest stable soliton'' is well-defined without circular reference to $m_e$ (e.g., from Axiom~4 saturation gradient + lattice cutoff alone). & Back-edges above; full-derivation chain Layer~8. \\
Flux-tube radial profile (Gaussian ansatz) & Vol~2 Ch.~2 Layer~6 (proton mass calculation) models the flux tube as a Gaussian LC resonant loop with FWHM $= \ell_{node}$, producing the exact $M/L = 1/\sqrt{2}$ mutual coupling at $d = \ell_{node}/2$ and the threshold $\rho_{threshold} = 1 + \ell_{node}/(8\sqrt{2\ln 2}) \approx 1.1062$ via standard Gaussian arithmetic. Result internally consistent given the ansatz. Axiom~1 fixes the FWHM but not the functional form. & Removes the Gaussian as a buried assumption. Requires either (a) deriving the Gaussian profile from Axiom~4 LC dynamics + transmission-line boundary conditions, or (b) replacing it with the framework-consistent profile (sech$^2$, Bessel $J_0$, algebraic $\sqrt{1-r^2}$ Axiom-4 kernel) and re-evaluating $\rho_{threshold}$ and $\mathcal{V}_{total}$. The empirical constraint $\mathcal{V}_{total} = 2.0$ (FEM-converged to $0.13\%$) and the proton mass agreement at $m_p/m_e \approx 1836.15$ remain binding on whatever profile emerges. & Vol~2 Ch.~2 §Saturation Threshold. \\
\bottomrule
\end{tabular}
\end{center}

These are the principal outstanding rigour gaps. They are not calculational errors elsewhere in the chain --- the chain itself is acyclic and the values it produces match experiment to the precision quoted in the master prediction table. Closing any of these gaps moves the ``structurally zero-parameter'' framing closer to absolute, without invalidating the existing predictions.