% =========================================================
% Appendix: Vacuum Engineering Design Specifications
% =========================================================
\chapter{Vacuum Engineering Design Specifications}
\label{app:vacuum_eng}

This appendix collects all engineering-critical design parameters derived throughout the volume into a structured reference. Each specification is traced to its axiomatic origin, with worked examples demonstrating the calculation chain from first principles to fabrication tolerance.

\section{Design Specification Protocol}

Every Design Specification in this volume follows a formal verification structure:

\begin{enumerate}
    \item \textbf{Axiomatic Origin:} The specification must trace to one or more of the four AVE axioms, the three calibration parameters ($\ell_{node}$, $\alpha$, $G$), or a previously derived intermediate result.
    \item \textbf{Solver Calibration:} If a specification is resolved numerically via a topological solver (e.g., extracting elastic moduli from an LC mesh), the solver must first demonstrably recover the standard CODATA/NIST measurements for purely covalent (e.g., Silicon) and purely van der Waals (e.g., Argon) canonical lattices to certify boundary neutrality.
    \item \textbf{Quantitative Bound:} The specification must produce a numerical value with explicit units and parameterization sweeps (modeling operating phase spaces such as temperature distributions and orientational phase locks).
    \item \textbf{Kill-Switch Condition:} If applicable, the specification defines a falsification boundary --- a numerical threshold beyond which the proposed architecture is structurally impossible.
\end{enumerate}

\noindent If all three tiers are satisfied, the parameter enters the Design Specification Datasheet with a green status. If the axiomatic chain is incomplete (e.g., requires an undone derivation), the parameter is flagged as ``Open Derivation.''

\section{Consolidated Design Parameters}
\label{sec:design_params}

\subsection{Universal Constants (Axiom-Derived)}

\begin{designbox}{Universal Vacuum Constants}
\begin{center}
\small
\begin{tabular}{l c c l}
\hline\hline
\textbf{Parameter} & \textbf{Symbol} & \textbf{Value} & \textbf{Axiom Source} \\
\hline
Lattice pitch & $\ell_{node}$ & $3.862 \times 10^{-13}$ m & Calibration \\
Fine-structure constant & $\alpha$ & 1/137.036 & Calibration \\
Vacuum impedance & $Z_0$ & $376.73\;\Omega$ & Axiom 2 ($\sqrt{\mu_0/\varepsilon_0}$) \\
Packing fraction (FCC) & $\phi_{crit}$ & 0.7405 & Axiom 1 ($\pi\sqrt{2}/6$) \\
Void fraction & $1 - \phi_{crit}$ & 0.2595 & Axiom 1 complement \\
Vacuum Poisson ratio & $\nu_{vac}$ & 2/7 & Axiom 2 ($K = 2G$) \\
Dielectric yield voltage & $V_{yield}$ & 43.65 kV & Axiom 4 ($\sqrt{\alpha} \cdot V_{snap}$) \\
Saturation operator & $S(x)$ & $\sqrt{1-x^2}$ & Axiom 4 ($n = 2$); A-034 \\
Hydrogen bond energy & $E_{HB}$ & 0.2158 eV & Axiom 4 $\times$ void fraction \\
\hline\hline
\end{tabular}
\end{center}
\end{designbox}

\noindent \textit{A-034 cross-scale note (canonical 2026-05-15 evening): the saturation operator $S(x) = \sqrt{1-x^2}$ above is the \textbf{Universal Saturation Kernel}, catalogued in 19 cross-scale instances spanning 21 orders of magnitude (atomic dielectric breakdown $\to$ BCS superconductivity at 0.00\% error $\to$ NOAA-validated solar flares $\to$ BH ring-down at 1.7\% from GR $\to$ cosmic K4 crystallization). See Vol 0: Engineering Compendium backmatter for the full A-034 catalog.}

\subsection{LLCP Metamaterial Parameters (Derived)}

\begin{designbox}{LLCP Metamaterial Specifications}
\begin{center}
\small
\begin{tabular}{l c l}
\hline\hline
\textbf{Parameter} & \textbf{Value} & \textbf{Status} \\
\hline
$n_{meta}(\phi)$ & $[1 - (\phi/\phi_{crit})^2]^{-1/2}$ & Derived (Ch.~2) \\
$K_{residual}$ (symmetric) & $K_0 \sqrt{2\delta}$ & Derived (Ch.~2) \\
$K_{residual}$ (asymmetric) & $f \cdot K_{wedge}$ & Derived (Ch.~2) \\
$Z_{meta}/Z_0$ (symmetric) & 1.000 & Derived (Ch.~2) \\
$Z_{meta}/Z_0$ (asymmetric) & $\sqrt{K_w/2G_w}$ & Derived (Ch.~2) \\
$\Delta \Gamma$ Isolation (per junction) & $-0.27$ dB (Non-Reciprocal) & Derived (Ch.~2 Cosserat FDTD) \\
Wedge $K_w/G_w$ ($C_{60}$) & $2.667 \to 1.667$ & Derived ($300$K--$4$K) \\
$f_{max}$ (Acoustic Bandwidth) & $2.04$ THz & Derived (Ch.~6 Memristor Limit) \\
\hline\hline
\end{tabular}
\end{center}
\end{designbox}

\subsection{Casimir Cavity Parameters (Derived)}

\begin{designbox}{Casimir Cavity Specifications}
\begin{center}
\small
\begin{tabular}{l c l}
\hline\hline
\textbf{Parameter} & \textbf{Value} & \textbf{Status} \\
\hline
Casimir pressure ($d = 5$ nm) & $2.1 \times 10^5$ Pa & Derived (Ch.~6) \\
Casimir pressure ($d = 1$ nm) & $1.3 \times 10^8$ Pa & Derived (Ch.~6) \\
Planarity tolerance ($d = 10$ nm) & $4\sigma/d < 0.04$ & Derived (Ch.~6, Kill-Switch) \\
Min.\ plate spacing & $d_{min} > \ell_{node}$ & Axiom 1 (lattice floor) \\
Metamaterial-enhanced spacing & $d^*_{meta} = n_{meta} \cdot d^*_{vac}$ & Derived (Ch.~8) \\
\hline\hline
\end{tabular}
\end{center}
\end{designbox}

\section{Worked Examples}
\label{sec:worked_examples}

\subsection{Example 1: Computing $n_{meta}$ for a Target Fabrication Gap}

\begin{examplebox}[$n_{meta}$ from a Target Plate Spacing]
\textbf{Given:} A Casimir qubit shield requires plate spacing $d_{fab} = 5$ nm. The vacuum critical spacing is $d^*_{vac} = 0.607$ pm.

\textbf{Required:} The LLCP packing fraction $\phi$ needed to achieve this spacing.

\textbf{Solution:}
\begin{enumerate}
    \item The required refractive index: $n_{meta} = d_{fab} / d^*_{vac} = 5 \times 10^{-9} / 6.07 \times 10^{-13} = 8{,}237$.
    \item From the Ch.~2 derivation: $n_{meta} = [1 - (\phi/\phi_{crit})^2]^{-1/2}$, so:
    \[
        \frac{\phi}{\phi_{crit}} = \sqrt{1 - \frac{1}{n_{meta}^2}} = \sqrt{1 - \frac{1}{8237^2}} = 1 - 7.4 \times 10^{-9}
    \]
    \item The required packing precision: $\delta = \phi_{crit} - \phi = 7.4 \times 10^{-9} \times 0.7405 \approx 5.5 \times 10^{-9}$.
\end{enumerate}
\end{examplebox}

\subsection{Example 2: Casimir Pressure Survivability Under Asymmetric Saturation}

\begin{examplebox}[Asymmetric Saturation Pressure Budget]
\textbf{Given:} A $C_{60}$-doped LLCP matrix with $K_{C60} \approx 12$ GPa, wedge volume fraction $f = 0.30$.

\textbf{Required:} Does the fill survive Casimir pressure at $d_{fab} = 5$ nm?

\textbf{Solution (Asymmetric):}
\begin{enumerate}
    \item Casimir pressure at 5 nm: $P_C = \pi^2 \hbar c / (240 \times d^4) = 2.1 \times 10^5$ Pa $\approx 2.1$ atm.
    \item Residual bulk modulus (asymmetric): $K_{residual} = f \cdot K_{wedge} = 0.30 \times 12 \times 10^9 = 3.6 \times 10^9$ Pa $= 3.6$ GPa.
    \item Ratio: $K_{residual}/P_C = 3.6 \times 10^9 / 2.1 \times 10^5 \approx 17{,}000$.
\end{enumerate}
\textbf{Result:} The wedge scaffold provides a safety factor of $\sim 17{,}000\times$ above the Casimir pressure at 5 nm. Under asymmetric saturation, the fill easily survives.

\textbf{Contrast (Symmetric):} Under symmetric saturation at this $n_{meta} \approx 8{,}237$, $K_{residual} \approx K_0 \sqrt{2\delta} \approx 600$ Pa $\ll P_C$. The fill is crushed. The symmetric architecture fails; the asymmetric architecture succeeds.
\end{examplebox}

\subsection{Example 3: Reading a Design Specification Datasheet}

\begin{examplebox}[Interpreting a Kill-Switch]
A Design Specification entry marked ``Kill-Switch'' defines a boundary beyond which the proposed device is structurally impossible under AVE axioms. For instance:

\begin{center}
\small
\begin{tabular}{l c l}
\hline\hline
\textbf{Parameter} & \textbf{Bound} & \textbf{Kill-Switch} \\
\hline
$C_{60}$ defect density & $< 7.8\%$ & Percolation threshold (Ch.~3) \\
Planarity $4\sigma/d$ & $< 0.04$ & Casimir uniformity (Ch.~6) \\
$n_{meta}$ (symmetric) & $< K_{0}/P_C(\delta)$ & Casimir crush (Ch.~8) \\
\hline\hline
\end{tabular}
\end{center}

If a fabrication process cannot achieve these bounds, the device does not fail ``gradually'' --- it fails \textbf{categorically}, because the underlying vacuum physics does not support the required mode structure outside these limits. This is the engineering advantage of axiom-derived specifications: there is no ambiguity about design margins.
\end{examplebox}

\section{Open Derivation Register}
\label{sec:open_derivations}

The following parameters have incomplete axiomatic derivation chains. Each represents a defined research frontier with a clear resolution path.

\begin{center}
\small
\begin{tabular}{l l l}
\hline\hline
\textbf{Parameter} & \textbf{Resolution Path} & \textbf{Priority} \\
\hline
\multicolumn{3}{c}{\textit{All parameters derived parameters derived organically from axioms}} \\
\hline\hline
\end{tabular}
\end{center}
