% eq_axiom_1.tex — Axiom 1 (Substrate Topology / Chiral Laves K4 Cosserat Crystal)
% Single source of truth. \input this wherever Axiom 1 is formally restated.
% Per canonical Scheme A: manuscript/vol_1_foundations/chapters/01_fundamental_axioms.tex:51-52.
%
% PROVENANCE:
% (1) Pre-2026-04-27 this file was titled "Axiom 1 — Impedance" and documented
%     the calibration constants Z_0 and ell_node. Per axiom homologation
%     2026-04-27, those constants are derived from Axiom 1 (not the axiom
%     itself); they have been moved to eq_calibration_constants.tex.
% (2) Pre-2026-05-16 the canonical name was "Chiral Laves K4 Crystal" with
%     Cosserat micropolar character bundled into the meaning. Per Grant
%     2026-05-16, renamed to "Chiral Laves K4 Cosserat Crystal" — the constitutive
%     nature (Cosserat = micropolar = nodes have intrinsic rotational DOF = source
%     of spin) is promoted into the name itself so a reader scanning the axiom
%     list immediately sees that nodes carry rotational/spin DOF in addition to
%     translational position. The shorter legacy form "Chiral Laves K4 Crystal"
%     remains a valid alias.
%
\begin{resultbox}{Axiom 1 — Substrate Topology (Chiral Laves K4 Cosserat Crystal)}
The physical vacuum IS a \textbf{chiral Laves K4 Cosserat crystal} $\mathcal{M}_A$ --- a 3D crystallized substrate of nodes at pitch $\ell_{node}$, governed by the right-handed $I4_1 32$ chiral space group, with 4-fold K4 nearest-neighbor connectivity at each node. Each node is \textbf{micropolar} (Cosserat-type), carrying \textbf{six intrinsic degrees of freedom} per node: three \textbf{translational} (capacitive coupling $\varepsilon_0$, identified with the electric field) and three \textbf{microrotational} (inductive coupling $\mu_0$, identified with the magnetic field). \textbf{The Cosserat microrotational DOF IS the substrate-native origin of intrinsic spin}: macroscopic angular momentum, the EM magnetic field $B$, and QM electron spin are three projections of the same per-node rotational coordinate. Spin is not added to the framework; it is what the rotational DOF is when the substrate is excited as a topological soliton. The intrinsic translation $\leftrightarrow$ E, rotation $\leftrightarrow$ B coupling makes every node a native LC oscillator: the substrate is structurally a Cosserat micropolar crystal AND a discrete LC resonant network, the same structural reality described in mechanical and electromagnetic terms. In the macroscopic continuum limit, the lattice is a \textbf{Trace-Reversed Chiral LC Network} supporting intrinsic spin and trace-free transverse EM wave propagation.

\medskip\noindent
\textbf{Two macroscopic substrate phases} (connected by Axiom 4's universal saturation kernel):
\begin{itemize}\itemsep 0pt
    \item \textbf{Crystallized phase} (current observable universe, Axiom 4 Regimes I--III): the chiral Laves K4 crystal supports linear EM wave propagation and topologically-quantized matter (particles as stable solitons per Axiom 2).
    \item \textbf{Ruptured plasma phase} (Axiom 4 Regime IV): K4 topology destroyed; no long-range order; found at black-hole event-horizon interiors and at the pre-crystallization cosmic state (before lattice genesis). Information dissipates thermally per Vol 3 Ch~\ref{ch:bh_interior} (BH Interior Regime IV).
\end{itemize}
The phase transition between the two states IS the A-034 universal strain-snap mechanism, occurring identically at every scale (atomic dielectric breakdown $\to$ BCS pair-condensate yield $\to$ geomagnetic reversal $\to$ solar flares $\to$ BH ring-down $\to$ cosmic K4 crystallization at lattice genesis).

\medskip\noindent
Classical mechanics and network dynamics are macroscopic effective theories of the substrate's bulk dynamics, not fundamental physical primitives.

\medskip\noindent
The numerical scale of this substrate is set by the calibration constants $Z_0 = \sqrt{\mu_0/\varepsilon_0}$ (vacuum impedance) and $\ell_{node} = \hbar/(m_e c)$ (lattice pitch); see \texttt{eq\_calibration\_constants.tex} for tabulated values.
\end{resultbox}
