% eq_axiom_2.tex — Axiom 2 (Topo-Kinematic Isomorphism)
% Single source of truth. \input this wherever Axiom 2 is formally restated.
% Per canonical Scheme A: manuscript/vol_1_foundations/chapters/01_fundamental_axioms.tex:54-59.
%
% PROVENANCE: pre-2026-04-27 this file was titled "Axiom 2 — Fine Structure" and
% documented the calibration constants alpha and V_yield. Per axiom homologation
% 2026-04-27, those constants are derived (alpha from Axiom 4's EMT operating
% point; V_yield from Axiom 4's saturation activation threshold); they have been
% moved to eq_calibration_constants.tex. This file now states the canonical
% primitive Axiom 2 from Vol 1 Ch 1.
%
\begin{resultbox}{Axiom 2 — Topo-Kinematic Isomorphism}
Charge $q$ is a discrete geometric dislocation in the $\mathcal{M}_A$ network. The Burgers vector of this dislocation IS the lattice pitch $\ell_{node}$, so the fundamental dimension of charge is identical to length ($[Q] \equiv [L]$). The macroscopic scaling is the Topological Conversion Constant:
\begin{equation}
    \xi_{topo} \equiv \frac{e}{\ell_{node}} \quad \text{[Coulombs / Meter]}
    \label{eq:axiom2_xi_topo}
\end{equation}
Numerical value $\xi_{topo} \approx 4.149 \times 10^{-7}$ C/m; see \texttt{eq\_calibration\_constants.tex}.

\medskip\noindent
\textbf{Charge quantization} follows directly: dislocation Burgers vectors must respect the K4 lattice (Axiom 1), so charge is quantized in integer multiples of $e$. \textbf{Charge sign} is the handedness of the dislocation in the substrate's chiral $I4_1 32$ structure --- particles and antiparticles are the two parity-related Burgers vectors permitted by the lattice geometry.

\medskip\noindent
\textbf{Fractional charges (Witten effect).} The $\mathbb{Z}_3$ symmetry of Borromean three-strand topology splits a unit dislocation into three linked sub-dislocations carrying $\pm 1/3\, e$ and $\pm 2/3\, e$. This is the substrate-native origin of quark fractional charges.

\medskip\noindent
\textbf{Topological solitons of this dislocation field are particles:} the $(2,3)$ torus knot is the electron (whose Q-factor at the Golden Torus geometry derives $\alpha = 1/137.036$, Vol 1 Ch 8), $(2,5)$ cinquefoil the proton, and the $(2,q)$ family generates the baryon ladder (Vol 2 Ch 2).

\medskip\noindent
\textbf{Namespace caveat.} The Topological Conversion Constant $\xi_{topo}$ above is distinct from two other $\xi$ symbols in the framework: (a) Vol 3 Ch 1's Machian $\xi \sim 10^{38}$ (cosmological-scale impedance boundary, derived $G = \hbar c / (7 \xi m_e^2)$), and (b) Q-G47 Sessions 9-18's substrate-scale Cosserat prefactors $\xi_{K1}, \xi_{K2}$ with $\xi_{K2}/\xi_{K1} = 12$ (K4-symmetry-forced). See \texttt{xi-topo-traceability.md} for the namespace de-collision.
\end{resultbox}
