% eq_axiom_3.tex — Axiom 3 (Gravity)
% Single source of truth. \input this wherever Axiom 3 is formally restated.
%
\begin{resultbox}{Axiom 3 — Gravity}
Newton's constant sets the Machian boundary impedance:
\begin{equation}
    G = \frac{\hbar c}{7\xi \cdot m_e^2}
    \label{eq:axiom3_gravity}
\end{equation}
where $\xi = 4\pi(R_H / \ell_{node})\alpha^{-2} \approx 8.15 \times 10^{43}$ is the Machian hierarchy coupling.
The gravitational refractive index is
\begin{equation}
    n(r) = 1 + \frac{2GM}{rc^2}
    \label{eq:axiom3_refraction}
\end{equation}
with Symmetric Gravity: $\mu_{eff} = \mu_0 \cdot n(r)$,\;
$\varepsilon_{eff} = \varepsilon_0 \cdot n(r)$,\;
$Z = Z_0$ (invariant).
\end{resultbox}

\noindent\textbf{Derived Consequence 1: $\alpha$ Invariance.}
Under Symmetric Gravity, both constitutive parameters scale by the same factor $n \cdot S$
(including Axiom~4 saturation). The fine-structure constant is therefore
\textit{exactly invariant} under gravitational strain:
\begin{equation}
    \alpha = \frac{e^2}{4\pi\,\varepsilon_{local}\,\hbar\,c_{local}}
           = \frac{e^2}{4\pi\,(\varepsilon_0 n S)\,\hbar\,(c_0/(nS))}
           = \frac{e^2}{4\pi\,\varepsilon_0\,\hbar\,c_0}
           = \alpha_0
    \label{eq:alpha_invariance}
\end{equation}
Multi-species clock comparisons at different gravitational potentials predict a
\textbf{null result} for $\Delta\alpha/\alpha$, consistent with all current experimental bounds.

\noindent\textbf{Derived Consequence 2: Temporal vs.\ Spatial Lattice Compression.}
The principal radial strain $\varepsilon_{11} = 7GM/(c^2 r)$ compresses the lattice asymmetrically.
The refractive index decomposes into:
\begin{equation}
    n_{temporal} = 1 + \tfrac{2}{7}\,\varepsilon_{11} \quad (\text{controls clock rate, redshift})
    \qquad
    n_{spatial} = \tfrac{9}{7}\,\varepsilon_{11} \quad (\text{controls light deflection})
    \label{eq:lattice_decomposition}
\end{equation}
Axiom~3 uses only the temporal component for gravitational redshift ($z \approx GM/(c^2 r)$).
The spatial component governs light bending and frame dragging.

