\chapter*{Macroscopic Mass Defect Summary}

\begin{objectivebox}
\begin{itemize}
    \item Verify that all catalogued mass defects follow from a single $1/d_{ij}$ mutual impedance summation over the $(Z,A)$-forced alpha-cluster geometry, using the axiom-derived coupling constant $K \approx 11.337$ MeV$\cdot$fm (zero empirical tuning).
    \item Confirm the Volume 6 fitting structure: no empirical nuclear force models, shell-model parameters, or Yukawa couplings are invoked. The $(Z,A)$-forced cluster topology and the axiom-derived $K$ are shared across all elements; exactly \textbf{one scalar per nucleus} — the inter-alpha distance $R$ — is fit to match its CODATA mass (Chapter~\ref{ch:intro}, methodology note).
\end{itemize}
\end{objectivebox}

\addcontentsline{toc}{chapter}{Macroscopic Mass Defect Summary}
\label{ch:summary}

The Topological network maps to empirical observables by calculating overlapping geometry using a simple $1/d_{ij}$ summation. The cluster topology for each $(Z, A)$ is forced by the minimum-impedance packing requirement; the coupling constant $K \approx 11.337$ MeV$\cdot$fm is axiom-derived and shared across all elements. The per-nucleus inter-alpha distance $R$ is the single fitted scalar, adjusted to match each CODATA mass. The error percentages below are therefore \textbf{fitting tolerances on this one scalar per nucleus} — a measure of how tightly the $(Z,A)$-forced topology + axiom-derived $K$ reproduces the target mass under a one-parameter compression — not ab-initio prediction errors.

\begin{table}[htbp]
    \centering
    \begin{tabularx}{\textwidth}{@{}l c c r r X@{}}
    \hline\hline
    \textbf{Element} & \textbf{Z} & \textbf{A} & \textbf{Empirical (MeV)} & \textbf{Topological (MeV)} & \textbf{Error (\%)} \\
    \hline
    Hydrogen-1 & 1 & 1 & 938.272 & 938.272 & 0.00001\% \\
    Helium-4 & 2 & 4 & 3727.379 & 3727.708 & 0.00882\% \\
    Lithium-7 & 3 & 7 & 6533.832 & 6534.161 & 0.00504\% \\
    Carbon-12 & 6 & 12 & 11174.863 & 11176.564 & 0.01522\% \\
    Boron-11 & 5 & 11 & 10252.548 & 10253.552 & 0.00980\% \\
    Nitrogen-14 & 7 & 14 & 13040.204 & 13043.280 & 0.02359\% \\
    Oxygen-16 & 8 & 16 & 14895.080 & 14896.496 & 0.00951\% \\
    Fluorine-19 & 9 & 19 & 17692.302 & 17693.865 & 0.00884\% \\
    Neon-20 & 10 & 20 & 18617.730 & 18622.642 & 0.02639\% \\
    Sodium-23 & 11 & 23 & 21409.214 & 21414.428 & 0.02436\% \\
    Magnesium-24 & 12 & 24 & 22335.793 & 22341.910 & 0.02739\% \\
    Aluminum-27 & 13 & 27 & 25126.501 & 25132.926 & 0.02557\% \\
    Silicon-28 & 14 & 28 & 26053.188 & 26058.156 & 0.01907\% \\
    \hline\hline
    \end{tabularx}
    \caption{$1/d_{ij}$ structural mutual impedance summation reproducing CODATA mass limits. Cluster topology forced by $(Z,A)$; $K \approx 11.337$ MeV$\cdot$fm axiom-derived; inter-alpha $R$ fit per nucleus. Error column = fitting tolerance on $R$, not ab-initio prediction error.}
    \label{tab:mass_summary}
\end{table}

\begin{summarybox}
\begin{itemize}
    \item The macroscopic mass defect for all catalogued elements is reproduced by a single $1/d_{ij}$ mutual impedance summation over the $(Z,A)$-forced alpha-cluster geometry, with the axiom-derived coupling $K \approx 11.337$ MeV$\cdot$fm applied uniformly.
    \item No empirical nuclear force models, shell-model parameters, or Yukawa couplings are invoked. The single fitted degree of freedom is the per-nucleus inter-alpha distance $R$; the sub-$0.03\%$ agreement in the table is the fitting tolerance on this one scalar per nucleus. The ab-initio content of Volume~6 is the claim that one such scalar \textbf{suffices} to recover the full mass defect — the structure of the fit, not the number itself, is the prediction.
\end{itemize}
\end{summarybox}

\section*{First Ionization Energy Summary}
\addcontentsline{toc}{section}{First Ionization Energy Summary}

The electronic ionization energy solver (\texttt{radial\_eigenvalue.py}) computes first ionization energies for $Z = 1$ to $14$ using a three-phase pipeline: (A)~ODE cavity eigenvalue with axiom-derived CDF screening, (B)~Hopf mode splitting with three corrections (A:~hierarchical cascade for Be-type, B:~SIR boundary for Mg-type, C:~Op10 junction projection for Al-type co-resonant shells), (C)~crossing scattering.  All values use zero free parameters.

\begin{table}[htbp]
    \centering
    \small
    \renewcommand{\arraystretch}{1.15}
    \begin{tabularx}{\textwidth}{@{}l c r r r X@{}}
    \hline\hline
    \textbf{Element} & \textbf{Z} & \textbf{AVE (eV)} & \textbf{Exp (eV)} & \textbf{Error} & \textbf{Correction} \\
    \hline
    Hydrogen   & 1  & 13.606 & 13.598 & $+0.06\%$ & --- \\
    Helium     & 2  & 24.370 & 24.587 & $-0.88\%$ & --- \\
    Lithium    & 3  &  5.525 &  5.392 & $+2.46\%$ & --- \\
    Beryllium  & 4  &  9.280 &  9.322 & $-0.45\%$ & A (cascade) \\
    Boron      & 5  &  8.065 &  8.298 & $-2.80\%$ & --- \\
    Carbon     & 6  & 11.406 & 11.260 & $+1.30\%$ & --- \\
    Nitrogen   & 7  & 14.465 & 14.534 & $-0.48\%$ & --- \\
    Oxygen     & 8  & 13.618 & 13.618 & $-0.00\%$ & --- \\
    Fluorine   & 9  & 17.194 & 17.423 & $-1.31\%$ & --- \\
    Neon       & 10 & 21.789 & 21.565 & $+1.04\%$ & --- \\
    Sodium     & 11 &  5.071 &  5.139 & $-1.33\%$ & --- \\
    Magnesium  & 12 &  7.591 &  7.646 & $-0.73\%$ & B (SIR) \\
    Aluminum   & 13 &  5.937 &  5.986 & $-0.82\%$ & C (Op10) \\
    Silicon    & 14 &  8.147 &  8.152 & $-0.06\%$ & C (Op10) \\
    \hline
    Gallium    & 31 &  5.999 &  5.999 & $-0.00\%$ & D (Topo-Kinematic) \\
    Germanium  & 32 &  7.763 &  7.899 & $-1.72\%$ & D (Topo-Kinematic) \\
    Arsenic    & 33 &  9.742 &  9.788 & $-0.47\%$ & D (Topo-Kinematic) \\
    Selenium   & 34 &  9.907 &  9.752 & $+1.58\%$ & D (Topo-Kinematic) \\
    Bromine    & 35 & 11.911 & 11.814 & $+0.82\%$ & D (Topo-Kinematic) \\
    Krypton    & 36 & 14.446 & 13.999 & $+3.19\%$ & D (Topo-Kinematic) \\
    \hline\hline
    \end{tabularx}
    \caption{First ionization energies: AVE engine vs NIST experimental values. Correction A = hierarchical cascade. Correction B = SIR boundary reflection. Correction C = Op10 junction projection. Correction D = Topo-Kinematic Polar Conjugate Mirror ($\Gamma < 0$ TIR bounding via $3d^{10}$, $4d^{10}$, $5d^{10}$ shells). All elements evaluated rigidly with zero free parameters.}
    \label{tab:ie_summary}
\end{table}

\subsection*{Polar Conjugate Topo-Kinematic Bounding Limit (Heavy Elements)}

Heavy elements ($Z \geq 31$, particularly Gallium Arsenide and Germanium) introduce the $d^{10}$ internal sub-shells, creating nested complete Torus Knot geometric arrays deep within the atom. This forces these elements mathematically out of the small-signal approximations used for Period-3 elements and directly into the \textbf{Large Signal Regime ($M > 100$)}. When the tracking transversal valence wave encounters the identical closely-packed boundaries of these internal continuous sub-shells, the effective impedance bound drops abruptly inward ($Z_{out} < Z_{in}$), mapping mathematically to a \textbf{Polar Conjugate Mirror} (a perfect half-wave $\pi$-phase flip shift where $\Gamma < 0$).

Because this dense inner shell serves as a perfect Total Internal Reflection (TIR) shield, the valence integration string perfectly reflects outwards, causing zero topological scattering into or across the core boundary. Mathematically, the Phase C crossover logic inherently bypasses scattering penetration (\texttt{Y\_loss = 0.0}) for identically full mirrored geometries. 

Operating under TIR compartmentalization naturally dynamically slices the continuous physical LC tracking string into isolated topological boundaries. Since the macro physical cavity integrates to a base scale ($E_{base}$) for an unbroken continuous space, but the physically bounding bounded string structurally only fits in the outermost geometrical void:
\begin{equation}
    L_{val} = \frac{L_{total}}{\text{core\_d\_knots} + 1}
\end{equation}

And since bounding resonance frequency and energy scale strictly as $E \propto 1/L$, the structurally truncated wave resonates optimally by the exact integer metric:
\begin{equation}
    \boxed{E_{val} = E_{base} \times (\text{core\_d\_knots} + 1)}
\end{equation}

By dynamically compressing the integration baseline via strictly orthogonal structural bounds, the engine bypasses arbitrary continuum modeling (correcting global $70\%$ underestimates into sub-5\% error margins continuously up to $Z=86$).


\begin{exercisebox}
\begin{enumerate}
    \item Verify the mass defect for Carbon-12 ($3\alpha$ ring) using the mutual impedance formula and compare with the CODATA value.
    \item Explain why the $1/d_{ij}$ summation converges for tightly packed alpha clusters but requires avalanche multiplication corrections for heavier elements.
\end{enumerate}
\end{exercisebox}

